### 2021-02-14 results.tex
additional review to the results section

\begin{figure}[htb]
  \centering{
  \includegraphics[trim=60 20 0 50,scale=0.7]{images/venn-plot-1.pdf}}
  \caption{Venn Diagram highlighting how the sandboxes from the tools can
    complement each other.}
  \label{fig:venn-plot1}
\end{figure}

@@

Additionally, we investigate if we could benefit from combining
the results from FlowDroid and DroidFax. Figure~\ref{}
shows the results.
Considering the static analysis provided by DroidFax and FlowDroid, our results showed that both were able to detect 33 pairs in common (34.37\%), and there were 29 pairs that both were not able to detect (30.20\%). We also realized that just 9 pairs were detected by DroidFax and do not by FlowDroid, while 25 pairs were detected by FlowDroid, and do not by DroidFax, evincing a better accuracy of tainted analysis algorithm.

The first results show that with tainted analysis, we had an analysis processing cost of 32.08 seconds per app pair on average, totaling a processing time of 52 minutes to analyze all the pairs. The processing time depends on the size of the app, and the pair that took the fastest time analyzed in 3 seconds and the longest 437 seconds.

Table \ref{tab:comparison} compile the results of this comparison.

\begin{table}[htb]
\centering
\begin{tabular}{lcc}\toprule

Detected by  & Malwares detected & \%   \\ 
(DroidFax/FlowDroid) & (Among 96 pair) & \\ \midrule
Both tools & 33 & 34.37\%  \\
Just DroidFax & 9 &  \\
Just FlowDroid & 25 &  \\
None & 29 & 30.20\% \\\midrule

\multicolumn{1}{r}{Total} &   96 \\ \bottomrule
\end{tabular} 
\caption{Comparison between DroidFax and FlowDroid algorithms}
\label{tab:comparison}
\end{table}

Furthermore, we can highlight that among 19 pair apps that at first study, were not detected by the sandboxes constructed by test generation tool, and static analysis DroidFax miner, 4 were detected by FlowDroid; P35, P38, P56, and P94, therefore exposing better accuracy of the tainted analysis algorithms. Among these 4 pairs detected, 2 were trojans, 1 was the exploit, and 1 was adware.

>>>>

\begin{figure}[htb]
  \centering{
  \includegraphics[trim=60 20 0 50,scale=0.7]{images/venn-plot-s1-1.pdf}}
  \caption{Venn Diagram highlighting how the sandboxes from the tools can
    complement each other.}
  \label{fig:venn-plot1}
\end{figure}

@@

Additionally, we investigate if we could benefit from combining
the results from FlowDroid and DroidFax. Figure~\ref{fig:venn-plot2} shows a
Venn-diagram summarizing the results. So, when combining
the results from FlowDroid and DroidFax, we were able to detect
67 of the malicious apps (69.79\%), a performance compatible
to that we found as response to the first execution of the
test case generation tools---which also considers the DroidFax
static analysis algorithms. More interesting, from those 67
malicious apps identified, 33 pairs had been found by
both tools (FlowDroid and DroidFax), even though they follow
a completely different static analysis approach. Furthermore,
FlowDroid shows to bem more effective than DroidFax, detecting 25 malicious
apps that had not been detected by DroidFax (while DroidFax detected nine
malicious apps that had not been detected by FlowDroid).

\begin{finding}
  Integrating the results of static analysis tools
  (such as FlowDroid and DroidFax) seems promising,
  leading to a performance similar to that achievend
  when combining test case generation tools with the
  DroidFax tool. 
\end{finding}

\begin{figure}
  \centering{
  \includegraphics[trim=60 20 0 50,scale=0.7]{images/venn-plot-s2-1.pdf}}
  \caption{Venn Diagram highlighting the possible benefits of
    integrating FlowDroid and DroidFax.}
  \label{fig:venn-plot2}

\end{figure}

The execution of FlowDroid is also feasible: the analysis takes only
32.08 seconds per app on average, totaling a processing time of 52
minutes to analyze all 96 pairs of Android apps.
Even though the time to execute the FlowDroid analysis depends on the size
of the app, the longest run took only 437 seconds.

Finally, we can highlight that FlowDroid was able to detect four malwares among the 19 malicious Android apps that had not
been detected by the sandboxes constructed in the first study. Among these
four malwares, two are \emph{trojans}, 1 is an \emph{exploit}, and 1
is an \emph{adware}.

\begin{finding}
  Although FlowDroid presents a performance similar
  to that of using the dynamic analysis approach for mining sandboxes,
  it was able to detect only four additional malwares (out of the
  19) that had not been detected in the first study. 
\end{finding}

\rb{This is a nice place to present some details about the malwares
  that FlowDroid had detected, showin the additional source-sink pairs
  that emmerged. A discussion about these aforementioned four pairs would
  also be relevant.}

\rb{I finished my first review until this place. Tomorrow I will continue
from here.}
